イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-07-13 Paper.tex
add: first commit

\title[イーサリアム: A Secure Decentralised Generalised Transaction Ledger\\ \smaller \textbf{{Berlin version}}]{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}

>>>>

\title[イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version}}]{イーサリアム: 安全な分散型汎用トランザクション台帳\\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}}
\author{
    Dr. Gavin Wood\\
    Founder, Ethereum \& Parity\\
    gavin@parity.io
}
\begin{document}
